---
title: "Combined Cleaning and Joining File"
output: html_document
---

```{r}
library(dplyr)
library(lubridate)
library(stringr)
library(hexbin)
library(tidyr)
library(tidyverse)

```
**Upload the CSV files for NOx, Ozone, and Kestrel data**
```{r}
#OZONE DATA
ozoneintfile <- read.csv("https://raw.githubusercontent.com/wyattjssmith/CMSC205-Project/master/ARTEMIS_ALEX_TimeSeries%20CMSC%20205%20Ozone%20sheet.csv?token=AXxYxYDTyOR5hgSSXsCaLx7AaEWcd_hdks5YzsUhwA%3D%3D")

#KESTREL DATA
Kestrelintfile <- read.csv("https://raw.githubusercontent.com/wyattjssmith/CMSC205-Project/master/ARTEMIS_ALEX_TimeSeries%20CMSC%20205%20Kestrel.csv?token=AXxYxVMVP0UBFC5fNOsx7TZVLaVxneyCks5YzDrSwA%3D%3D", as.is = TRUE, header = TRUE)

#NOx DATA
raw_nox <- read.csv("https://raw.githubusercontent.com/wyattjssmith/CMSC205-Project/master/Clean_NOx.csv?token=AX51v2i8LsGZFEkRiUAxoVxeA7GFQicpks5YxeRPwA%3D%3D")
```
**Tidying Ozone Data**
```{r}
ozoneintfile <- ozoneintfile[-c(1:4), -8] #Remove first four rows with header information in them and last column with NAs

colnames(ozoneintfile) <- c("ozone_log_num", "ozone_ppm", "ozone_cell_temp", "ozone_cell_pressure", "ozone_flow_rate", "date", "time")
ozone2 <- unite(ozoneintfile, date_time, date, time, sep = " ")

ozone2$date_time <- as.character(ozone2$date_time)
ozone2$date_time<- str_sub(ozone2$date_time, 1, nchar(ozone2$date_time) -3)


ozone2$ozone_log_num <- as.numeric(ozone2$ozone_log_num)
ozone2$ozone_ppm <- as.numeric(ozone2$ozone_ppm)
ozone2$ozone_cell_temp <- as.numeric(ozone2$ozone_cell_temp)
ozone2$ozone_cell_pressure <- as.numeric(ozone2$ozone_cell_pressure)
ozone2$ozone_flow_rate <- as.numeric(ozone2$ozone_flow_rate)

#Parameterizing data to remove obvious outliers based on previous plotting and observations



ozone2 <- filter(ozone2, ozone_ppm < 1000, ozone_ppm > -15)
ozone2 <- filter(ozone2, ozone_flow_rate < 20000, ozone_flow_rate > 350)
ozone2 <- filter(ozone2, ozone_cell_pressure < 600)

# ggplot(ozone2, aes(y = ozone_cell_temp, x = date_time)) + geom_point()
# ggplot(ozone2, aes(y = ozone_cell_pressure, x = date_time)) + geom_point()
# ggplot(ozone2, aes(y = ozone_cell_pressure, x = date_time)) + geom_point(color = "navy") + labs(title = "Ozone Cell Pressure Across the Month After Filtering", y = "Ozone Cell Pressure", x = "Date") + theme_gray()
#Did not feel comfortable filtering temp


#Did filtering before grouping to not lose minutes of data
ozone2_group <- group_by(ozone2, date_time)
```
**Grouping Ozone Data and averaging to the minute**
```{r}
avg_ozone <- ozone2_group %>%
  summarize("ozone_log_num" = mean(ozone_log_num), 'ozone_ppm' = mean(ozone_ppm), 'ozone_cell_temp' = mean(ozone_cell_temp),  'ozone_cell_pressure' = mean(ozone_cell_pressure), 'ozone_flow_rate' = mean(ozone_flow_rate))

avg_ozone$date_time <- mdy_hm(avg_ozone$date_time)

```

**Tidying NOx Data**
```{r}
#Already ran these once, running str_sub again will change Time slot again
raw_nox$Time <- as.character(raw_nox$Time)
raw_nox$Time <- str_sub(raw_nox$Time, 1, nchar(raw_nox$Time) - 3)

#Join together Date and Time
raw_nox <- unite(raw_nox, date_time, Date, Time, sep = " ")

#Make date_time a date
raw_nox$date_time <- mdy_hm(raw_nox$date_time)

#Other stuff imported from original doc
nox <- raw_nox

#Make everything numeric!
nox$X <- as.numeric(nox$X)
nox$i.Model.405 <- as.numeric(nox$i.Model.405)
nox$NO2 <- as.numeric(nox$NO2)
nox$NO <- as.numeric(nox$NO)
nox$NOx <- as.numeric(nox$NOx)
nox$ZnO2 <- as.numeric(nox$ZnO2)
nox$ZnO <- as.numeric(nox$ZnO)
nox$Cf <- as.numeric(nox$Cf)
nox$Cell.Temp <- as.numeric(nox$Cell.Temp)
nox$Cell.Pressure <- as.numeric(nox$Cell.Pressure)
nox$Overflow <- as.numeric(nox$Overflow)
nox$Cell.Flow <- as.numeric(nox$Cell.Flow)
nox$Ozone.Flow <- as.numeric(nox$Ozone.Flow)
nox$PDVa <- as.numeric(nox$PDVa)
nox$PDVb <- as.numeric(nox$PDVb)
nox$PDVo3 <- as.numeric(nox$PDVo3)
nox$Scrubber.Temp <- as.numeric(nox$Scrubber.Temp)
#Don't do this!!!!!!!!!! nox$date_time <- as.numeric(nox$date_time)
nox$Mode <- as.numeric(nox$Mode)
#Parameterizing NOx data to reomve outliers
raw_nox <- filter(raw_nox, raw_nox$Cell.Pressure > 700)
raw_nox <- filter(raw_nox, raw_nox$NO2 < 4000)
raw_nox <- filter(raw_nox, raw_nox$Cell.Flow > 1675)

#Group each data set into minutes and call it new_nox
new_nox<-nox%>%
  group_by(date_time)%>%
summarize('X' = mean(X), 'i.Model.405' = mean(i.Model.405), 'NO2' = mean(NO2), 'NO' = mean(NO), 'NOx' = mean(NOx), 'ZnO2' = mean(ZnO2), 'ZnO' = mean(ZnO), 'Cf' = mean(Cf), 'nox_cell_temp' = mean(Cell.Temp), 'Cell.Pressure' = mean(Cell.Pressure), 'Overflow' = mean(Overflow), 'nox_cell_flow' = mean(Cell.Flow), 'ozone_flow' = mean(Ozone.Flow), 'PDVa' = mean(PDVa), 'PDVb' = mean(PDVb), 'PDVo3' = mean(PDVo3), 'scrubber_temp' = mean(Scrubber.Temp), 'Mode' = mean(Mode))
```

**Plots used to set parameters for NOx**
```{r}
# raw_nox%>%
#   ggplot(aes(x = date_time, y = Cell.Flow)) + geom_point(color = 'purple')
# 
# raw_nox%>%
#   ggplot(aes(x = date_time, y = Cell.Pressure)) + geom_point(color = 'purple')
# 
# raw_nox%>%
#   ggplot(aes(x = date_time, y = NO2)) + geom_point(color = 'purple')
```

**Joinging NOx and Ozone**
**Remove commented out function and change to desired name to gain a joined csv**
```{r}
nox_ozone <- inner_join(x = avg_ozone, y = new_nox, by = "date_time")

# write.csv(nox_ozone, "Joined NOx and Ozone file.csv")
```

**Tidying Kestrel Data**
```{r}

collabs<- Kestrelintfile[3, ]
Kestrel<-Kestrelintfile[5:45511, ]
names(Kestrel)<- collabs
b <- Kestrel[- c(1:21177),]
preformat <- Kestrel[- c(21174:45511), ]
preformat$`FORMATTED DATE_TIME` <- as.character(preformat$`FORMATTED DATE_TIME`)
preformat$`FORMATTED DATE_TIME`<-str_sub(preformat$`FORMATTED DATE_TIME`, 1,(nchar(preformat$`FORMATTED DATE_TIME`)-3))

b$`FORMATTED DATE_TIME` <- mdy_hm(b$`FORMATTED DATE_TIME`)
preformat$`FORMATTED DATE_TIME` <- mdy_hm(preformat$`FORMATTED DATE_TIME`)

Kestrelt<- rbind(b, preformat)
Kestrelt$`FORMATTED DATE_TIME` <- ymd_hms(Kestrelt$`FORMATTED DATE_TIME`)


Kestrelt$`FORMATTED DATE_TIME` <- as.character(Kestrelt$`FORMATTED DATE_TIME`)
Kestrelt$`FORMATTED DATE_TIME`<-str_sub(Kestrelt$`FORMATTED DATE_TIME`, 1,(nchar(Kestrelt$`FORMATTED DATE_TIME`)-3))



Kestrelt$`Barometric Pressure`<- as.numeric(Kestrelt$`Barometric Pressure`)
Kestrelt$`Density Altitude`<- as.numeric(Kestrelt$`Density Altitude`)
Kestrelt$Headwind <- as.numeric(Kestrelt$Headwind)
Kestrelt$`Direction - True` <- as.numeric(Kestrelt$`Direction - True`)
Kestrelt$`Wind Speed`<- as.numeric(Kestrelt$`Wind Speed`)
Kestrelt$`Wind Chill` <- as.numeric(Kestrelt$`Wind Chill`)
Kestrelt$`Direction - Mag` <- as.numeric(Kestrelt$`Direction - Mag`)
Kestrelt$`Station Pressure`<- as.numeric(Kestrelt$`Station Pressure`)
Kestrelt$`Dew Point`<- as.numeric(Kestrelt$`Dew Point`)
Kestrelt$Crosswind<- as.numeric(Kestrelt$Crosswind)
Kestrelt$Altitude<- as.numeric(Kestrelt$Altitude)
Kestrelt$`Relative Humidity`<- as.numeric(Kestrelt$`Relative Humidity`)
Kestrelt$Temperature<- as.numeric(Kestrelt$Temperature)
Kestrelt$`Psychro Wet Bulb Temperature`<- as.numeric(Kestrelt$`Psychro Wet Bulb Temperature`)
Kestrelt$`Heat Stress Index`<-as.numeric(Kestrelt$`Heat Stress Index`)

colnames(Kestrelt)[1] <- "date_time"


new_kestrel<-group_by(Kestrelt, date_time) %>%
summarize( "barometric_pressure" = mean(`Barometric Pressure`), "density_altitude" = mean(`Density Altitude`), "headwind" = mean(Headwind), "directtrue" = mean(`Direction - True`), "windspeed" = mean(`Wind Speed`), "windchill" = mean(`Wind Chill`), "directmag" = mean(`Direction - Mag`), "statpress" = mean(`Station Pressure`), "dewpoint" = mean(`Dew Point`), "crosswind" = mean(Crosswind), "altitude" = mean(Altitude), "relativehum" = mean(`Relative Humidity`), "temp" = mean(Temperature), "psychrowetbulb" = mean(`Psychro Wet Bulb Temperature`), "heatstressindex" = mean(`Heat Stress Index`))


new_kestrel$date_time <- ymd_hm(new_kestrel$date_time)
```


** Joining the data for Kestrel, Ozone, and NOx**
**Remove commented out function and change to desired name to gain a joined csv**
```{r}
ARTEMIS_data <- inner_join(x = new_kestrel, y = nox_ozone, by = "date_time")



colnames(ARTEMIS_data) <- c("Date Time", "Barometric Pressure (mb)", "Density Alititude (m)", "Headwind (m/s)", "Direction - True", "Wind Speed (m/s)", "Wind Chill (°C)", "Direction Magnitude", "Station Pressure (mb)", "Dew Point (°C)", "Cross Wind (m/s)", "Altitude (m)", "Relative Humidity (%)", "Temperature (°C)", "Psychro Wet Bulb Temperature (°C)", "Heat Stress Index (°C)", "Ozone Log Number", "Ozone Concentration (ppm)", "Ozone Cell Temperature (°C)", "Ozone Cell Pressure", "Ozone Flow Rate", "Garbage", "NOx Log Number", "NO2 Concentration (ppm)", "NO Concentration (ppm)", "NOx Concentration (ppm)", "ZnO2", "ZnO", "NOx Cf", "NOx Cell Temperature (°C)", "NOx Cell Pressure","NOx Overflow", "NOx Cell Flow", "Ozone Flow", "PDVa", "PDVb", "PDVo3", "Scrubber Temperature (°C)", "NOx Mode")


# write.csv(ARTEMIS_data,"ARTEMIS_Test_Data.csv")
```
**To Joing Additional Data**
Make Sure the Data has a date_time column and is tidy (run it through the necessary chunk)
```{r}
#Additional_data <- inner_join(X, Y, by = "date_time")

# Set X and Y as the necessary dataframes
```

